---
output: github_document
---

# breaker
This package contains functions to work with different line break options.
For now, I only wrote a function: `nbreak()`.   

### nbreak
The `nbreak()` function can be very useful when you want to break lines of a string recursively, or just break a once.

### Instalation
```{r}
devtools::install_github("igorkf/breaker")
library(breaker)
```

### Usage
```{r}
knitr::opts_chunk$set(fig.width = 11, collapse = T, comment = "#>")
library(tidyverse)

nbreak(string = "I want to break lines until the end of this sentence, every 3 lines", n = 3, loop = T) %>% cat()
nbreak(string = "I don't like to jump too much!", n = 3, loop = F) %>% cat()
```
Note that we're setting `fig.width = 11` to show longer plots.

The function simply adds `\n` between the words:
```{r}
nbreak(string = "I want to break lines until the end of this sentence, every 3 lines", n = 3, loop = T)
```
If your word is not a multiple from the `n` argument, there's no problem. The function will run until the end of the sentence.
Note that `loop = TRUE` by default.

### An example
```{r}
tibble(a1 = sample(c("I don't know", "Right", "Wrong"), size = 30, replace = T, prob = c(0.4, 0.3, 0.3))) %>% 
ggplot(aes(x = a1, fill = a1)) +
geom_bar() +
labs(title = "Thats a title!") +
theme_bw() +
theme(legend.position = "none")
```
That's seems good, right? But if you wanted to do it for a lot of plots that have big texts?

******

We'll use these answers of a questionary:
```{r}
#This package allows you to stick multiple charts side by side:
#install.packages("cowplot")

titles <- c("1- Disrespect the traffic signs, going beyond when the traffic light indicates the red light, is an attitude:",
            "2 - If someone, during the recess of school, finds money lying on the ground, that person should:",
            "3- Use false student ID to pay half-entry into an event, it's an attitude:")

tab <- tibble(a1 = sample(c("I only drive my bicycle (and I'm afraid of)", "Right", "Wrong"), size = 30,
                          replace = T, prob = c(0.4, 0.3, 0.3)),
a2 = sample(c("Find the owner", "I would take all the money and don't tell anybody"), size = 30,
            replace = T, prob = c(0.7, 0.3)),
a3 = sample(c("Wrong", "Right", "I really don't know"), size = 30,
            replace = T, prob = c(0.3, 0.3, 0.4)))

ans <- tab %>% colnames()

#ans is getting into x and titles into y:
map2(ans, titles,
    ~ggplot(tab, aes(x = !!sym(.x), fill = !!sym(.x))) +
      geom_bar() +
      labs(title = .y) +
      theme_bw() +
      theme(legend.position = "none",
      title = element_text(size = 10))) %>% 
cowplot::plot_grid(plotlist = ., ncol = 3)
```
Look up this mess!


We can make a function (just to be easier to put in map2) and fix it up:
```{r, fig.width = 11}
gg <- function(data, x, y){
data %>%
  mutate_all(. %>% map_chr(., ~nbreak(.x, n = 3))) %>% 
  as.data.frame() %>% 
  ggplot(aes(x = !!sym(x), fill = !!sym(x))) +
    geom_bar() +
    labs(title = nbreak(string = y, n = 6)) +
    theme_bw() +
    theme(legend.position = "none",
    title = element_text(size = 10))
}

map2(ans, titles, ~gg(tab, .x, .y)) %>% 
  cowplot::plot_grid(plotlist = ., ncol = 3)
```
